%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Dr. rer. nat. Physics} % Degree
    {Technical University of Munich} % Institution
    {Munich, Germany} % Location
    {2016 -- 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Advisor: PD Dr. Oliver Kortner.}
        \item {Thesis: \href{https://cds.cern.ch/record/2744557}{Search for Dark Matter Produced in Association with Hadronically Decaying Bosons at \(\sqrt{s}\)~=~13\,TeV with the ATLAS Detector at the LHC}.}
      \end{cvitems}
    }

  \cventry
    {Master of Science in Physics (Nuclear, Particle and Astrophysics)} % Degree
    {Technical University of Munich} % Institution
    {Munich, Germany} % Location
    {2013 -- 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Advisor: PD Dr. Oliver Kortner.}
        \item {Thesis: \href{https://cds.cern.ch/record/2162398}{Development of a Concept for the Muon Trigger of the ATLAS Detector at the HL-LHC}.}
        \item {Passed with distinction.}
      \end{cvitems}
    }

    \cventry
    {Erasmus+ Student Mobility for Studies} % Degree
    {University of Edinburgh} % Institution
    {Edinburgh, United Kingdom} % Location
    {Winter 13} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Courses (reported with ECTS, grade/mark): Philosophy of Science 1 (10 ECTS, B/64), Musical Acoustics (10 ECTS, A1/93), Quantum Physics (5 ECTS, A1/96), Quantum Theory (5 ECTS, A3/74), Relativistic Quantum Field Theory (5 ECTS, D/42).}
      \end{cvitems}
    }

    \cventry
    {Teaching Degree for Upper Secondary Education “Gymnasiallehramt” (not completed)} % Degree
    {Ludwig Maximilian University of Munich} % Institution
    {Munich, Germany} % Location
    {2012 -- 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {With subjects physics, mathematics, and educational science.}
        \item {Completed educational science part (36/36 ECTS) and in­ten­si­ve in­ternship (duration of 1 year, com­bi­na­ti­on of SPS I and SPS II), partially completed mathematics part (66/105 ECTS) and physics part (84/105 ECTS), dropout in favour of PhD studies.}
      \end{cvitems}
    }

  \cventry
    {Bachelor of Science in Physics} % Degree
    {Technical University of Munich} % Institution
    {Munich, Germany} % Location
    {2010 -- 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Advisor: Prof. Dr. Laura Fabbietti.}
        \item {Thesis: \href{https://www.das.ktas.ph.tum.de/DasDocs/Public/Bachelor_Theses/thesis_Gadow.pdf}{dE/dx studies with pion and electron tracks of the ALICE GEM IROC prototype}.}
        \item {Passed with merit.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
