%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Outreach \& Professional Development}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\cvsubsection{Professional Memberships}

  \begin{small} \color{black}
  Deutsche Physikalische Gesellschaft \\
  Alumni der Studienstiftung des deutschen Volkes e. V. \\
  \end{small}


\cvsubsection{Formal Training in Media and Communication}

\begin{cvhonors}

  %---------------------------------------------------------
    \cvhonor
      {Science Communication for CERN Guides} % Course
      {(16.08.2023), 4-hour long training, covering introduction to science communication and key communication skills.} % Course
      {CERN} % Location
      {2023} % Date(s)
  
  %---------------------------------------------------------
    \cvhonor
      {CERN Guide Training} % Course
      {(04.05.2023), course offered by CERN Visits Service.} % Position
      {CERN} % Location
      {2023} % Date(s)
  
  %---------------------------------------------------------
  \cvhonor
  {Workshop Science Communication} % Course
  {(27./28.10.2022), two-day workshop offered by NaWik (National Institute for Science Communication) as award for participation in "KlarText Preis für Wissenschaftskommunikation" competition.} % Position
  {NaWik} % Location
  {2022} % Date(s)

  %---------------------------------------------------------
    \cvhonor
      {"Rhetorik extrem"} % Course
      {(21.06.2017 -- 23.06.2017), intensive course offered by the TUM Graduate School.} % Position
      {TUM} % Location
      {2017} % Date(s)
  
  %---------------------------------------------------------
    \cvhonor
      {City Guide Training} % Course
      {(28.09.2014 -- 13.04.2015), training course for becoming a city guide for the city of Munich.} % Committee
      {Weis(s)er Stadtvogel} % Location
      {2014 -- 2015} % Date(s)
  
  %---------------------------------------------------------
    \cvhonor
      {"Überzeugend auftreten – auch in schwierigen Situationen"} % Course
      {(09.07.2012), course offered by "ProLehre (TUM)".} % Committee
      {TUM} % Location
      {2012} % Date(s)
  
  %---------------------------------------------------------
    \cvhonor
      {"Erfolgreich präsentieren – Präsentieren wie Steve Jobs?"} % Course
      {(30.11.2011), course offered by "ProLehre (TUM)".} % Committee
      {TUM} % Location
      {2011} % Date(s)

  %---------------------------------------------------------
  \end{cvhonors}
  

\cvsubsection{Science Communication}

\begin{cvpubs}
  \cvpub{\textbf{Public talks}}
\end{cvpubs}

\begin{cvhonors}
  %---------------------------------------------------------
    \cvhonor
      {Keynote Talk for Higgs Boson Discovery 10th Anniversity} % Event/Organization
      {"Inspired by Higgs" at DESY / University of Hamburg. \href{Link to recording}{https://www.youtube.com/watch?v=sNs97If8vdw}.} % Position
      {} % Location
      {04.07.2022} % Date(s)
      
  %---------------------------------------------------------
    \cvhonor
      {Symposium on Science Communication} % Event/Organization
      {"Science Slams as a method of science communication" at Hamburg Research Academy.} % Position
      {} % Location
      {28.04.2022} % Date(s)

\end{cvhonors}

\begin{cvpubs}
  \cvpub{\textbf{CERN Science Show Presenter:} CERN science shows are theatre-style presentations delivered by CERN scientists that promote science with interactive experiments. Each show lasts 50 min
  and has up to 200 visitors. In June 2024 I will have presented 9 science shows.}
\end{cvpubs}

\begin{cvpubs}
  \cvpub{\textbf{CERN Guide and ATLAS Underground Guide:} CERN official guides provide tours to the general public and private visitor groups. In June 2024 I will have guided 24 private visits and 5 group visits.}
\end{cvpubs}

\begin{cvpubs}
  \cvpub{\textbf{ATLAS Virtual Visits:} ATLAS virtual visits are live video connections where a CERN
  scientist guides a group through the ATLAS experiment, presenting its research, and answering
  audience questions directly from the ATLAS control room or the detector underground. In June
  2024 I will have guided 7 virtual visits.}
\end{cvpubs}

\begin{cvpubs}
  \cvpub{\textbf{ATLAS Masterclasses:} The ATLAS Masterclass programme is an educational outreach initiative that enables secondary
  school students to engage directly with particle physics. Students learn fundamental research
  methods by analysing measurements from actual collision events recorded by the ATLAS
  experiment.}
\end{cvpubs}

\begin{cvhonors}
%---------------------------------------------------------
\cvhonor
{ATLAS masterclass project day with lecture and experiments on particle physics} % Event/Organization
{Munich, Germany} % Position
{Bavaria, Germany} % Location
{02.05.2019} % Date(s)   

%---------------------------------------------------------
\cvhonor
{ATLAS masterclass project day with lecture and experiments on particle physics} % Event/Organization
{Bavaria, Germany} % Position
{} % Location
{09.04.2019} % Date(s)   

%---------------------------------------------------------
\cvhonor
{ATLAS masterclass project day with lecture and experiments on particle physics} % Event/Organization
{Bavaria, Germany} % Position
{} % Location
{22.07.2016} % Date(s)   

\end{cvhonors}

\begin{cvpubs}
  \cvpub{\textbf{Netzwerk Teilchenwelt Teacher Training Programme:} I have imparted
  practical knowledge on cloud chamber experiments during teach-the-teacher training sessions for
  Bavarian teachers in the Bavarian state's teacher training centre in Gars am Inn.}
\end{cvpubs}

\begin{cvpubs}
  \cvpub{\textbf{3 minute thesis" competition judge} in panel for Hamburg Research Academy on 28.07.2022.}
\end{cvpubs}

\begin{cvpubs}
  \cvpub{\textbf{Science Slams} are competetive events in which scientists present their research in a given time frame to a diverse audience in an entertaining way. I participated in over 30 such events with a \href{https://www.youtube.com/watch?v=ZBDvvXhFoZg}{talk about dark matter searches at the Large Hadron Collider}, including the Southern German championship. In 2022, I organised a two-day science communication workshop about science communication for doctoral researchers at DESY.}
\end{cvpubs}

\begin{cvhonors}
%---------------------------------------------------------
\cvhonor
{Science Slam Planetarium Berlin} % Event/Organization
{Berlin, Germany} % Position
{} % Location
{10.07.2024} % Date(s)   
  %---------------------------------------------------------
  \cvhonor
    {Die große Science-Show im Juni} % Event/Organization
    {Unterföhring, Germany} % Position
    {} % Location
    {28.06.2024} % Date(s)
    
%---------------------------------------------------------
  \cvhonor
    {Science Slam University of Fribourg} % Event/Organization
    {Fribourg, Switzerland} % Position
    {} % Location
    {23.05.2024} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {Science Slam Public Library Munich} % Event/Organization
    {Munich, Germany} % Position
    {} % Location
    {01.07.2022} % Date(s)    

  %---------------------------------------------------------
  \cvhonor
    {1st PIER Science Slam} % Event/Organization
    {Hamburg, Germany} % Position
    {} % Location
    {04.05.2022} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {Einstein Slam, "Highlights der Physik"} % Event/Organization
    {Würzburg, Germany} % Position
    {} % Location
    {30.09.2021} % Date(s)    

%---------------------------------------------------------
  \cvhonor
    {Productronica Science Slam} % Event/Organization
    {Munich, Germany} % Position
    {} % Location
    {20.11.2019} % Date(s)    

%---------------------------------------------------------
  \cvhonor
    {Science Slam Esslingen} % Event/Organization
    {Esslingen, Germany} % Position
    {} % Location
    {23.10.2019} % Date(s)    

%---------------------------------------------------------
\cvhonor
{Science Kabarett in Seidlvilla Munich} % Event/Organization
{Munich, Germany} % Position
{} % Location
{12.06.2019} % Date(s)    

%---------------------------------------------------------
\cvhonor
{Science Slam Schaffhausen} % Event/Organization
{Schaffhausen, Switzerland} % Position
{} % Location
{06.04.2019} % Date(s)    

%---------------------------------------------------------
\cvhonor
{German Physics Society "Einstein Slam"} % Event/Organization
{Regensburg, Germany} % Position
{} % Location
{01.04.2019} % Date(s)    

%---------------------------------------------------------
\cvhonor
{Science Slamm Lippstadt} % Event/Organization
{Lippstadt, Germany} % Position
{} % Location
{21.02.2019} % Date(s)   

%---------------------------------------------------------
\cvhonor
{Science Show Grafing} % Event/Organization
{Grafing, Germany} % Position
{} % Location
{24.01.2019} % Date(s)   

%---------------------------------------------------------
\cvhonor
{Materialprüfungsanstalt Stuttgart} % Event/Organization
{Stuttgart, Germany} % Position
{} % Location
{17.10.2018} % Date(s)   

%---------------------------------------------------------
\cvhonor
{Max Planck Society "Max Planck Tag" Science Slam} % Event/Organization
{Munich, Germany} % Position
{} % Location
{14.09.2018} % Date(s)   

%---------------------------------------------------------
\cvhonor
{Munich Science Slam in Burda Bootcamp Munich} % Event/Organization
{Munich, Germany} % Position
{} % Location
{26.06.2018} % Date(s)   

%---------------------------------------------------------
\cvhonor
{"Faust Slam" Central Public Library Munich} % Event/Organization
{Munich, Germany} % Position
{} % Location
{15.06.2018} % Date(s)   

%---------------------------------------------------------
\cvhonor
{Science Slam in Lustspielhaus Munich} % Event/Organization
{Munich, Germany} % Position
{} % Location
{13.05.2018} % Date(s)   

%---------------------------------------------------------
\cvhonor
{"Turm der Sinne Slam" Nuremberg} % Event/Organization
{Nuremberg, Germany} % Position
{} % Location
{14.04.2018} % Date(s)   

%---------------------------------------------------------
\cvhonor
{Science Slam Planetarium Berlin} % Event/Organization
{Berlin, Germany} % Position
{} % Location
{11.04.2018} % Date(s)   

%---------------------------------------------------------
\cvhonor
{Science Slam in "Heppel und Ettlich" Munich} % Event/Organization
{Munich, Germany} % Position
{} % Location
{26.03.2018} % Date(s)   

%---------------------------------------------------------
\cvhonor
{Dornier Aircraft Yard Science Slam Friedrichshafen} % Event/Organization
{Friedrichshafen, Germany} % Position
{} % Location
{22.03.2018} % Date(s)   

%---------------------------------------------------------
\cvhonor
{Science Slam Michelstadt} % Event/Organization
{Michelstadt, Germany} % Position
{} % Location
{21.03.2018} % Date(s)   

%---------------------------------------------------------
\cvhonor
{Science Slam Roxy Ulm} % Event/Organization
{Ulm, Germany} % Position
{} % Location
{06.02.2018} % Date(s)   

%---------------------------------------------------------
\cvhonor
{Science Slam Chemiepark Gendorf} % Event/Organization
{Gendorf, Germany} % Position
{} % Location
{02.02.2018} % Date(s)   

%---------------------------------------------------------
\cvhonor
{Science Slam Studio Theatre Munich} % Event/Organization
{Munich, Germany} % Position
{} % Location
{25.01.2018} % Date(s)   

%---------------------------------------------------------
\cvhonor
{Science Slam at University of Clausthal-Zellerfeld} % Event/Organization
{Clausthal-Zellerfeld, Germany} % Position
{} % Location
{17.11.2017} % Date(s)   

%---------------------------------------------------------
\cvhonor
{Science Slam "Übel und gefährlich" Hamburg} % Event/Organization
{Hamburg, Germany} % Position
{} % Location
{25.10.2017} % Date(s)   

%---------------------------------------------------------
\cvhonor
{Southern German Championship 2017 Alte Feuerwache Mannheim} % Event/Organization
{Mannheim, Germany} % Position
{} % Location
{07.10.2017} % Date(s)   

%---------------------------------------------------------
\cvhonor
{Science Slam Weingarten} % Event/Organization
{Weingarten, Germany} % Position
{} % Location
{06.05.2017} % Date(s)   

%---------------------------------------------------------
\cvhonor
{Science Slam "Affentheater"} % Event/Organization
{Gießen, Germany} % Position
{} % Location
{03.11.2016} % Date(s)   

%---------------------------------------------------------
\cvhonor
{Science Slam Vereinsheim Munich} % Event/Organization
{Munich, Germany} % Position
{} % Location
{05.12.2014} % Date(s)   

%---------------------------------------------------------
\cvhonor
{Science Slam "Affentheater"} % Event/Organization
{Gießen, Germany} % Position
{} % Location
{06.11.2014} % Date(s)   

%---------------------------------------------------------
\cvhonor
{TUM Young Academy Science Slam at Deutsches Museum Munich} % Event/Organization
{Munich, Germany} % Position
{} % Location
{24.07.2014} % Date(s)   

\end{cvhonors}

% \cvsubsection{Peer Review}

% \begin{small} \color{black}
% One journal I review for \\
% Another journal \\
% \end{small}
