%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Mentoring}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\cvsubsection{(Co-)Supervision of Graduate Students}

\begin{cvhonors}

%---------------------------------------------------------
  \cvhonor
    {Dr. Alicia Wongel} % Name
    {PhD student co-supervised with Dr. Krisztian Peters.} % Relationship
    {University of Hamburg} % Location
    {2020 -- 2022} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {Elisaveta Sitnikova} % Name
    {PhD student co-supervised with Dr. Krisztian Peters.} % Relationship
    {University of Hamburg} % Location
    {2022 -- 2023} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {Jackson Barr} % Name
    {PhD student co-supervised with Dr. Krisztian Peters and Prof. Tim Scanlon.} % Relationship
    {UCL} % Location
    {2022 -- 2023} % Date(s)

%---------------------------------------------------------
\end{cvhonors}


\cvsubsection{(Co-)Supervision of Undergraduate Students}

\begin{cvhonors}
%---------------------------------------------------------
  \cvhonor
    {Milica Rajčić} % Name
    {CERN Summer Student Project, "Characterisation of the H2M monolithic pixel sensor ASIC".} % Relationship
    {University of Montenegro} % Location
    {2024} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {Maya Kvaratskhelia} % Name
    {Boston Student Programme Project, "Improved lepton isolation for \(H(ZZ^{\ast})\) measurements".} % Relationship
    {Notre Dame University} % Location
    {2024} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {Laura Winkler} % Name
    {Master Thesis Project, "Improved detection of charm jets using charged \(D^{\ast}\)-mesons".} % Relationship
    {University of Geneva} % Location
    {2023 -- 2024} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {Stefan Katsarov} % Name
    {DESY Summer Student Project, "Jet flavour tagging project with training a deep-sets-based algorithm to identify \(b\)-jets".} % Relationship
    {University of Edinburgh} % Location
    {2022} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {John Lawless} % Name
    {DESY Summer Student Project, "Machine learning techniques for top quark reconstruction in four-top-quark final states".} % Relationship
    {Iowa State University} % Location
    {2021} % Date(s)
%---------------------------------------------------------
\end{cvhonors}
