%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentations}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
\cvsubsection{Invited Talks}
%-------------------------------------------------------------------------------

\begin{cvpubs}
    \cvpub{July 2023. \textit{Heavy flavor jet tagging algorithms in ATLAS}. Invited talk: To b or not to b - CMS BTV Workshop 2023, Brussels, Belgium.\\\href{https://indico.cern.ch/event/1274182/contributions/5458302/}{https://indico.cern.ch/event/1274182/contributions/5458302/}.}
    
    \cvpub{Feb 2020. \textit{Dark matter searches with the ATLAS detector at the LHC}. Seminar talk: Cavendish Laboratory HEP Seminar, Cambridge, United Kingdom.}
\end{cvpubs}

%-------------------------------------------------------------------------------
\cvsubsection{International Conferences}
%-------------------------------------------------------------------------------

\begin{cvpubs}
    \cvpub{Mar 2024. \textit{A Scalable Platform for Training and Inference Using Kubeflow at CERN}. Workshop talk: Kubeflow Summit Europe, Paris, France.\\\href{https://sched.co/1YFhA/}{https://sched.co/1YFhA/}.}

    \cvpub{Feb 2024. \textit{Educational Outreach with AI-Assisted CERN Open Data Analysis}. Workshop talk: 1st Large Language Models in Physics Symposium, Hamburg, Germany.\\\href{https://indico.desy.de/event/38849/contributions/162122/}{https://indico.desy.de/event/38849/contributions/162122}.}

    \cvpub{Jul 2023. \textit{Searches for new phenomena in final states with 3rd generation quarks using the ATLAS detector}. Conference talk: SUSY2023, Southampton, United Kingdom.\\\href{https://indico.cern.ch/event/1214022/contributions/5461065/}{https://indico.cern.ch/event/1214022/contributions/5461065/}.}

    \cvpub{Jul 2022. \textit{Searches for new phenomena in final states with 3rd generation quarks using the ATLAS detector}. Conference talk: PHENO2023, Pittsburgh, United States of America.\\\href{https://indico.cern.ch/event/1089132/contributions/4855516/}{https://indico.cern.ch/event/1089132/contributions/4855516/}.}

    \cvpub{Jul 2019. \textit{ATLAS Highlights on Dark Matter Searches in Exotic Models}. Conference talk: XIII International Workshop on Interconnections between Particle Physics and Cosmology, Cartagena, Columbia.}

    \cvpub{Oct 2018. \textit{Search for dark matter produced in association with a Higgs boson decaying to bb}. Young Scientist Forum talk: Puzzle of Dark Matter Workshop, DESY Hamburg, Germany.\\\href{https://indico.desy.de/event/19155/contributions/34313/}{https://indico.desy.de/event/19155/contributions/34313/}.}

    \cvpub{Jun 2018. \textit{Search for Dark Matter in association with a hadronically decaying Z' vector boson with the ATLAS detector in pp collisions at 13 TeV}. Poster: Sixth Annual Conference on Large Hadron Collider Physics, Bologna, Italy.\\\href{https://indico.cern.ch/event/681549/contributions/2956249/}{https://indico.cern.ch/event/681549/contributions/2956249/}.}
\end{cvpubs}

%-------------------------------------------------------------------------------
\cvsubsection{National Conferences}
%-------------------------------------------------------------------------------

\begin{cvpubs}
    \cvpub{Sep 2019. \textit{Signal reweighting using BDTs}. Parallel talk: ATLAS Germany Meeting, Munich, Germany.\\\href{https://indico.cern.ch/event/811522/contributions/3541796}{https://indico.cern.ch/event/811522/contributions/3541796}.}

    \cvpub{Mar 2019. \textit{Dark Matter + Mono-h(bb): How to get rid of the multijet background using the object-based \(E_{\textrm{T}}^{\textrm{miss}}\) significance}. Parallel talk: DPG spring meeting, Aachen, Germany.}

    \cvpub{Sep 2018. \textit{Object-based \(E_{\textrm{T}}^{\textrm{miss}}\) significance in Mono-H(\(\overline{b}b\))}. Parallel talk: ATLAS Germany Meeting, Freiburg, Germany.\\\href{https://indico.cern.ch/event/700593/contributions/3092043/}{https://indico.cern.ch/event/700593/contributions/3092043/}.}

    \cvpub{Mar 2018. \textit{Search for Dark Matter produced in association with a hadronically decaying W or Z boson with ATLAS Run-2 data}. Parallel talk: DPG spring meeting, Würzburg, Germany.}

    \cvpub{Mar 2017. \textit{Search for Dark Matter produced in association with a hadronically decaying W or Z boson with ATLAS Run-2 data}. Parallel talk: DPG spring meeting, Münster, Germany.}

    \cvpub{Mar 2017. \textit{Development of a new Level-0 Muon Trigger for the ATLAS Experiment at High-Luminosity-LHC}. Parallel talk: DPG spring meeting, Münster, Germany.}

    \cvpub{Mar 2016. \textit{Development of fast track reconstruction algorithms for the ATLAS MDT-precision-chamber-based Level-0 Muon Trigger at HL-LHC}. Parallel talk: DPG spring meeting, Hamburg, Germany.}

    \cvpub{Mar 2016. \textit{Study of the MDT-precision-chamber-based Level-0 Muon Trigger selectivity for the ATLAS experiment at HL-LHC}. Parallel talk: DPG spring meeting, Hamburg, Germany.}
\end{cvpubs}
