%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Teaching Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\cvsubsection{Formal Pedagogical Training}

\begin{cventries}

  %---------------------------------------------------------
      \cventry
      {Educational science and Psychology for Upper Secondary Education Teaching Degree   “Gymnasiallehramt”} % Degree
      {Ludwig Maximilian University of Munich} % Institution
      {Munich, Germany} % Location
      {2012 -- 2016} % Date(s)
      {
        \begin{cvitems} % Description(s) bullet points
          \item {Formal education in pedagogics through completed educational science and psychology part (36/36 ECTS) and in­ten­si­ve in­ternship at Gymnasium Neufahrn (duration of 1 year, com­bi­na­ti­on of SPS I and SPS II).}
        \end{cvitems}
      }
  
    \cventry
      {Undergraduate tutor qualification certificate} % Degree
      {Technical University of Munich} % Institution
      {Munich, Germany} % Location
      {2011 -- 2012} % Date(s)
      {
        \begin{cvitems} % Description(s) bullet points
          \item {Provided by the central scientific
          institution for Higher Education Teaching "ProLehre (TUM)" of the Technical University of Munich.}
          \item{61 work units, corresponding to a workload of 45 hours consisting of a
          basic training course for undergraduate tutors, a reflexion session, a conflict training and an open training course, as well as specialised workshops on exercise design, utilisation of blackboards and presentation training. The training was complemented by two teaching consultations.}
        \end{cvitems}
      }
  %---------------------------------------------------------
  \end{cventries}
  
  

\cvsubsection{University Teaching}

\begin{cvhonors}

%---------------------------------------------------------
  \cvhonor
    {Physikalisches Praktikum I für Studierende der Naturwissenschaften} % Course
    {Lab Course.} % Course
    {UHH} % Location
    {2025} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {Experimental Physics 2: Electromagnetism and Special Relativity} % Course
    {Tutorial.} % Course
    {TUM} % Location
    {2017} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {Experimental Physics 1: Mechanics} % Course
    {Tutorial.} % Position
    {TUM} % Location
    {2016/17} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {Tutorial: Experimental Physics 3: Optics} % Course
    {Tutorial.} % Position
    {TUM} % Location
    {2015/16} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {Experimental Physics 2: Electromagnetism and Special Relativity} % Course
    {Tutorial.} % Committee
    {TUM} % Location
    {2014} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {Experimental Physics 3: Optics} % Course
    {Tutorial.} % Committee
    {TUM} % Location
    {2013/14} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {Experimental Physics 2: Electromagnetism and Special Relativity} % Course
    {Tutorial.} % Committee
    {TUM} % Location
    {2012} % Date(s)
%---------------------------------------------------------
  \cvhonor
    {Mathematics for physicists 1: Linear Algebra} % Course
    {Tutorial.} % Committee
    {TUM} % Location
    {2012/13} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {Maths Introductory Course} % Course
    {for first-year students (three weeks).} % Committee
    {TUM} % Location
    {2012} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {Mathematics for physicists 1: Linear Algebra} % Course
    {Tutorial.} % Committee
    {TUM} % Location
    {2011/12} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {Maths Introductory Course} % Course
    {for first-year students (three weeks).} % Committee
    {TUM} % Location
    {2011} % Date(s)
%---------------------------------------------------------
\end{cvhonors}


\cvsubsection{Other Teaching}
\begin{cvhonors}
%---------------------------------------------------------
    \cvhonor
      {ATLAS Flavour Tagging Group Tutorials} % Course
      {Designed and supervised seven software tutorials for the ATLAS flavour tagging group. \href{Weblink}{https://ftag.docs.cern.ch/software/tutorials/}.} % Position
      {ATLAS} % Location
      {2021 -- 2023} % Date(s)
  %---------------------------------------------------------
    \cvhonor
      {ATLAS SUSY+HDBS+Exotics RECAST tutorial} % Course
      {Mentor for ATLAS virtual tutorial. \href{Indico agenda}{https://indico.cern.ch/event/1009271/}.} % Position
      {ATLAS} % Location
      {2021} % Date(s)
  %---------------------------------------------------------
    \cvhonor
      {CI/CD pipeline tutorial} % Course
      {Mentor for High Energy Physics Software Foundation virtual tutorial. \href{Indico agenda}{https://indico.cern.ch/event/904759/}.} % Position
      {HSF} % Location
      {2020} % Date(s)
  %---------------------------------------------------------
    \cvhonor
      {Docker training tutorial} % Course
      {Mentor for High Energy Physics Software Foundation virtual tutorial. \href{Indico agenda}{https://indico.cern.ch/event/934651/}.} % Position
      {HSF} % Location
      {2020} % Date(s)

  %---------------------------------------------------------
    \cvhonor
      {Secondary Education Teaching} % Course
      {"Lehr:werkstatt" intensive internship. Over the course of a year, I taught more than 250 hours in collaboration with an experienced teacher, independently prepared lessons, attended meetings and participated in school events.} % Position
      {Neufahrn Gymnasium, Germany} % Location
      {2014 -- 2015} % Date(s)
  %---------------------------------------------------------
\end{cvhonors}
