%!TEX encoding = UTF-8 Unicode
% CV LaTeX Template for CV/Resume
%
% This template has been downloaded and modified from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Modified (March 2019) by:
% Jessica A. Rick <jrick@uwyo.edu>
% http://www.jessicarick.com
% 
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, letterpaper, draft]{academic-cv}

% Configure page margins with geometry
\geometry{left=0.75in, top=0.75in, right=0.75in, bottom=0.75in, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
\name{Philipp Gadow}{}
\position{Research Associate {\enskip\cdotp\enskip}University of Hamburg}
\address{Office 113 b, Building 62, Luruper Chaussee 149, 22761 Hamburg, Germany}

\orcid{0000-0003-4475-6734}
\email{philipp.gadow@cern.ch}
\homepage{http://me.pgadow.de}
% \github{philippgadow}
% \extrainfo{extra informations}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal information
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {March 2025}
  {Philipp~·~Gadow ~~~ Curriculum Vitae}
  {\thepage}

\cvsection{Work history and education}
\begin{cventries}

  %---------------------------------------------------------
    \cventry
      {Research Staff} % Job title
      {University of Hamburg} % Institution
      {Hamburg, Germany} % Location
      {2024 -- Present} % Date(s)
      {
        \begin{cvitems} % Description(s) bullet points
          \item {Machine learning algorithms for jet flavour tagging, investigation of Higgs potential through searches for Higgs pair production, direct searches for dark matter with spherical proportional counters.}
          \item {Teaching, student supervision.}
        \end{cvitems}
      }

    \cventry
      {Senior Research Fellow} % Job title
      {CERN} % Institution
      {Meyrin, Switzerland} % Location
      {2023 -- 2024} % Date(s)
      {
        \begin{cvitems} % Description(s) bullet points
          \item {Searches for new phenomena in final states with top quarks, leadership of the ATLAS "Heavy Quarks, Top and Composite Higgs" physics sub-group, machine learning algorithms for jet flavour tagging and lepton isolation, silicon detector development for future collider experiments.}
          \item {Co-supervision of two undergraduate students and CERN summer students.}
        \end{cvitems}
      }
  
    \cventry
      {Quantum Universe Excellence Cluster Fellow} % Job title
      {Deutsches Elektronensynchrotron DESY} % Institution
      {Hamburg, Germany} % Location
      {2020 -- 2023} % Date(s)
      {
        \begin{cvitems} % Description(s) bullet points
          \item {Searches for heavy resonances with four-top-quark events, leadership of ATLAS "Flavour Tagging Algorithms" combined performance sub-group, reinterpretation of searches with active learning. }
          \item {Co-supervision of three PhD students and supervision of two summer students.}
        \end{cvitems}
      }
  
	  \cventry
	  {Dr. rer. nat. Physics} % Degree
	  {Technical University of Munich} % Institution
	  {Munich, Germany} % Location
	  {2016 -- 2020} % Date(s)
	  {
		\begin{cvitems} % Description(s) bullet points
		  \item {Advisor: PD Dr. Oliver Kortner.}
		  \item {Thesis: \href{https://cds.cern.ch/record/2744557}{Search for Dark Matter Produced in Association with Hadronically Decaying Bosons at \(\sqrt{s}\)~=~13\,TeV with the ATLAS Detector at the LHC}.}
		  \item {Tutor for experimental physics lectures and instructor for particle physics masterclasses in higher education schools.}
		\end{cvitems}
	  }
  
	\cventry
	  {Master of Science in Physics (Nuclear, Particle and Astrophysics)} % Degree
	  {Technical University of Munich} % Institution
	  {Munich, Germany} % Location
	  {2013 -- 2016} % Date(s)
	  {
		\begin{cvitems} % Description(s) bullet points
		  \item {Advisor: PD Dr. Oliver Kortner.}
		  \item {Thesis: \href{https://cds.cern.ch/record/2162398}{Development of a Concept for the Muon Trigger of the ATLAS Detector at the HL-LHC}.}
		  \item {Passed with distinction.}
		\end{cvitems}
	  }
  
	  \cventry
	  {Erasmus+ Student Mobility for Studies} % Degree
	  {University of Edinburgh} % Institution
	  {Edinburgh, United Kingdom} % Location
	  {Winter 13} % Date(s)
	  {
		\begin{cvitems} % Description(s) bullet points
		  \item {Courses (reported with ECTS, grade/mark): Philosophy of Science 1 (10 ECTS, B/64), Musical Acoustics (10 ECTS, A1/93), Quantum Physics (5 ECTS, A1/96), Quantum Theory (5 ECTS, A3/74), Relativistic Quantum Field Theory (5 ECTS, D/42).}
		\end{cvitems}
	  }
  
	  \cventry
	  {Teaching Degree for Upper Secondary Education “Gymnasiallehramt” (not completed)} % Degree
	  {Ludwig Maximilian University of Munich} % Institution
	  {Munich, Germany} % Location
	  {2012 -- 2016} % Date(s)
	  {
		\begin{cvitems} % Description(s) bullet points
		  \item {With subjects physics, mathematics, and educational science.}
		  \item {Completed educational science part (36/36 ECTS) and in­ten­si­ve in­ternship (duration of 1 year, com­bi­na­ti­on of SPS I and SPS II), partially completed mathematics part (66/105 ECTS) and physics part (84/105 ECTS), dropout in favour of PhD studies.}
		\end{cvitems}
	  }
  
	\cventry
	  {Bachelor of Science in Physics} % Degree
	  {Technical University of Munich} % Institution
	  {Munich, Germany} % Location
	  {2010 -- 2013} % Date(s)
	  {
		\begin{cvitems} % Description(s) bullet points
		  \item {Advisor: Prof. Dr. Laura Fabbietti.}
		  \item {Thesis: \href{https://www.das.ktas.ph.tum.de/DasDocs/Public/Bachelor_Theses/thesis_Gadow.pdf}{dE/dx studies with pion and electron tracks of the ALICE GEM IROC prototype}.}
		  \item {Passed with merit.}
		\end{cvitems}
	  }
  %---------------------------------------------------------
  \end{cventries}
  
\newpage

\input{../cv/honors.tex}

\cvsection{Positions of Responsibility}

\begin{cvhonors}

%---------------------------------------------------------
  \cvhonor
    {ATLAS Physics Exotics HQT sub-group convener} % Name
    {group consisting of ~100 members with 2 conveners.} % Relationship
    {} % Location
    {2024} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {ATLAS Control Room Shift Leader} % Name
    {overseeing data taking (over 50 shifts, of which in 2024: 23 shifts, in 2023: 24 shifts, and in 2022: 11 shifts).} % Relationship
    {} % Location
    {2022 -- 2024} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {ATLAS Combined Performance Flavour Tagging Algorithms
    sub-group convener} % Name
    {group consisting of ~30 members with 2 conveners.} % Relationship
    {} % Location
    {2021 -- 2023} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {ATLAS Physics Analysis Contact} % Name
    {for five analysis teams with teams consisting of between 5 to 40 members.} % Relationship
    {} % Location
    {2021 -- 2024} % Date(s)

%---------------------------------------------------------
\end{cvhonors}

\input{../cv/mentoring.tex}
\input{../cv/teaching.tex}


\cvsection{Science Communication}

\begin{cvpubs}
  \cvpub{\textbf{Public talks}}
\end{cvpubs}

\begin{cvhonors}
  %---------------------------------------------------------
    \cvhonor
      {Keynote Talk for Higgs Boson Discovery 10th Anniversity} % Event/Organization
      {"Inspired by Higgs" at DESY / University of Hamburg. \href{Link to recording}{https://www.youtube.com/watch?v=sNs97If8vdw}.} % Position
      {} % Location
      {04.07.2022} % Date(s)
      
  %---------------------------------------------------------
    \cvhonor
      {Symposium on Science Communication} % Event/Organization
      {"Science Slams as a method of science communication" at Hamburg Research Academy.} % Position
      {} % Location
      {28.04.2022} % Date(s)

\end{cvhonors}

\begin{cvpubs}
  \cvpub{\textbf{Science Slams} are competetive events in which scientists present their research in a given time frame to a diverse audience in an entertaining way. I participated in over 30 such events with a \href{https://www.youtube.com/watch?v=ZBDvvXhFoZg}{talk about dark matter searches at the Large Hadron Collider}, including the Southern German championship. In 2022, I organised a two-day science communication workshop about science communication for doctoral researchers at DESY.}

  \cvpub{\textbf{CERN Outreach:} I was involved in several outreach programmes during my time as a CERN fellow. These include science shows, theatre-style presentations delivered by CERN scientists that promote science with interactive experiments, lasting 50 min
  with up to 200 visitors. I have presented 9 science shows during my time at CERN. I was also active as a CERN Guide and ATLAS Underground Guide. I have guided 24 private visits and 5 group visits. I was also involved in ATLAS virtual visits, live video connections where a CERN
  scientist guides a group through the ATLAS experiment. I have guided 7 virtual visits during my time at CERN.}

  \cvpub{\textbf{"3 minute thesis" competition judge} in panel for Hamburg Research Academy on 28.07.2022.}

  \cvpub{\textbf{ATLAS Masterclasses:} The ATLAS Masterclass programme is an educational outreach initiative that enables secondary
  school students to engage directly with particle physics. Students learn fundamental research
  methods by analysing measurements from actual collision events recorded by the ATLAS
  experiment.}

  \cvpub{\textbf{Netzwerk Teilchenwelt Teacher Training Programme:} I have imparted
  practical knowledge on cloud chamber experiments during teach-the-teacher training sessions for
  Bavarian teachers in the Bavarian state's teacher training centre in Gars am Inn.}

\end{cvpubs}

\input{../cv/presentation.tex}
\input{../cv/publications.tex}

%-------------------------------------------------------------------------------
\end{document}
